PhoneLets: offloading the phone off your phone for energy, cost and network load optimization

### 2014-06-13 paper.tex
a few tweaks, wifi and 3g numbers adjusted for gs4

%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{PhoneLets: offloading the phone off your phone for energy, cost and network load optimisation}
\ifnum\anon=1
\author{[Paper: \#XXX]}% \hspace{0.2cm} \ampmtime ]}
\else
\numberofauthors{2}
\author{
% \alignauthor Andrius Aucinas\\
% \affaddr{University of Cambridge} 
% \and
% \alignauthor Jon Crowcroft\\
% \affaddr{University of Cambridge}
}
\fi
%for single author (just remove % characters)

@@

\section{Potential for energy efficiency}

@@

\begin{table}[t]
{
\small
\begin{tabular}{| l | c |}
\hline
  \textbf{Use case}         & \textbf{Avg. energy consumption (mA)}  \\ \hline
  Idle - airplane mode      & 5  \\ \hline
  Only BlueTooth on         & 6  \\ \hline
  Idle - only WiFi          & 8  \\ \hline
  Idle - 3G on              & 10 \\ \hline
  Apps background           & 22.4 - 54.5  \\ \hline
  WiFi Apps background      & ??    \\ \hline
  WiFi frequent messages    & YY    \\ \hline
  BT SIM access             & 28  \\ \hline
  WiFi tethering (idle)     & 80  \\ \hline
\end{tabular}
}
\caption{Energy consumption of the different usage scenarios of a mobile device.}
\label{tab:energy}
\end{table}

We measured energy consumption of a Samsung Galaxy S4 phone using the Power Monitor\footnote{Monsoon Power Monitor \url{http://www.msoon.com/LabEquipment/PowerMonitor/}}. The different values are presented in Table.~\ref{tab:energy}. Energy consumption of an idle device with applications in background (\emph{Apps background} considers a device with Google Apps, Skype, Facebook and Viber apps installed and running in background and is from our previous work~\cite{Aucinas:2013uk}.

@@

(1) \emph{Desk/table of approximately 2m$^2$} to accommodate the demo. (2) \emph{Two standard UK power sockets}. (3) \emph{Two cellular network subscriptions (SIM cards)}, but are to be sources by the presenters. Setup time - up to an hour for connecting the demo up and verifying operation. Other equipment includes a laptop, two smartphones and the custom-build hardware described above.

>>>>

%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{PhoneLets: offloading the phone off your phone for energy, cost and network load optimization}
\ifnum\anon=1
\author{[Paper: \#XXX]}% \hspace{0.2cm} \ampmtime ]}
\else
\numberofauthors{2}
\author{
\alignauthor Andrius Aucinas\\
\affaddr{University of Cambridge} 
\and
\alignauthor Jon Crowcroft\\
\affaddr{University of Cambridge}
}
\fi
%for single author (just remove % characters)

@@

\section{Energy saving opportunities}

@@

\begin{table}[t]
{
\small
\begin{tabular}{| l | c |}
\hline
  \textbf{Use case}         & \textbf{Avg. energy consumption (mA)}  \\ \hline
  Idle - airplane mode      & 5     \\ \hline
  Ifle - BlueTooth          & 6     \\ \hline
  Idle - WiFi               & 8     \\ \hline
  Idle - 3G                 & 10    \\ \hline
  Apps background - WiFi    & 27    \\ \hline
  BT SIM access             & 28    \\ \hline
  WiFi frequent messages    & YY    \\ \hline
  Apps background - 3G      & 40    \\ \hline
  WiFi tethering (idle)     & 80    \\ \hline
\end{tabular}
}
\caption{Energy consumption of the different usage scenarios of a mobile device.}
\label{tab:energy}
\end{table}

We measured energy consumption of a Samsung Galaxy S4 phone using the Power Monitor\footnote{Monsoon Power Monitor \url{http://www.msoon.com/LabEquipment/PowerMonitor/}}. The different values are presented in Table.~\ref{tab:energy}. Energy consumption of an idle device with applications in background (\emph{Apps background}) considers a device with Google Apps, and Facebook installed and running in background and is consistent with our earlier observations~\cite{Aucinas:2013uk}. We have only run the test on a single WiFi network, therefore we expect the figure to vary, especially because our used network is a public one with some background traffic affecting energy consumption of the device.

@@

(1) \emph{Desk/table of approximately 1.5m, standard-width} to accommodate the demo. (2) \emph{Two standard UK power sockets}. (3) \emph{Two cellular network subscriptions (SIM cards)}, but are to be sources by the presenters, (4) an HDMI display during setup. Setup time - up to an hour for connecting the demo up and verifying operation. Other equipment includes a laptop, two smartphones and the custom-build hardware described above.
